Prasanga Paudel- Data Analysis Project

### 2025-01-31 products/manuscript/Manuscript.qmd
changes in data summary

```{r, echo=FALSE, message=FALSE}
# load a few R packages
library(here)
library(knitr)
```

@@

## Description of data and data source
_This is a time series data based on 38 member countries from the Organisation for Economic Co-operation and Development (OECD). This organization is a unique forum with governments from 37 democracies collaborate to develop policy standards to promote sustainable economic growth. However, the data obtained from this dataset is crude and needs to be treated before attempting analysis based on it. For example, in its present form, the variable name is a long sentense describing the data it contains._

@@

## Data import and cleaning
_Write code that reads in the file and cleans it so it's ready for analysis. Since this will be fairly long code for most datasets, it might be a good idea to have it in one or several R scripts. If that is the case, explain here briefly what kind of cleaning/processing you do, and provide more details and well documented code somewhere (e.g. as supplement in a paper). All materials, including files that contain code, should be commented well so everyone can follow along._

## Statistical analysis
_Explain anything related to your statistical analyses._

>>>>

```{r, echo=FALSE, message=FALSE}
# load a few R packages
library(here)
library(knitr)
library(here)
library(readxl)
```

@@

## Description of data and data source
_This is a time series data based on 38 member countries from the Organisation for Economic Co-operation and Development (OECD). This organization is a unique forum with governments from 37 democracies collaborate to develop policy standards to promote sustainable economic growth. However, the data obtained from this dataset is crude and needs to be treated before attempting analysis based on it. For example, in its present form, the variable name is a long sentense describing the data it contains.The years are listed as column names and variables are listed as Series._

@@

## Data import and cleaning
```{r}
file_path <- here("data","raw-data", "wdi-oecd.xlsx")
data <- read_excel(file_path, sheet="Data")
```

## Statistical analysis

_This is the snapshot of the data as of now._
```{r}
head(data)
```
